
\begin{thebibliography}{Summnerville89}

\bibitem[Nygaard81]{nygaard81}K. Nygaard and O-J Dahl.  The Development
of the SIMULA language. In R. Wexelblat, editor, {\em History of
Programming Languages}, chapter IX, pages 439-493, Academic Press,
1981.

\bibitem[Waite86]{waite86}W. M. Waite. The cost of lexical analysis. {\em
Software --- Practice and Experience}, May 1986

\bibitem[Frase91]{frase91}Christopher W. Frase and David R, Hanson. A
Retargetable Compiler for ANSI C.  ACM SIGPLAN Notices, Volume 26, No.
10, October 1991

\bibitem[Sommerville89]{sommerville89}Ian Summerville, Software
Engineering, Third edition, Addison-Wesly, 1989

\bibitem[Dony90]{dony90}Christophe Dony, Exception Handling and
Object-Oriented Programming: towards a synthesis., ECOOP/OOPSLA '90
Proceedings

\bibitem[Grogono91]{grogono91}Peter Grogono, Issues in the Design of an Object
Oriented Programming Language, Structured Programming, January 1991

\bibitem[Amsterdam91]{amsterdam}Jonathan Amsterdam, Taking Exception 
to C, BYTE, August 1991

\bibitem[Cheung]{cheung}Peter Grogono and Benjamin Cheung, A Semantic Browser
for Object Oriented Program Development

\bibitem[Meyer88]{meyer88}Bertrand Meyer, Object-oriented Software
Construction, Prentice Hall, 1988

\bibitem[Fisher88]{fisher88}Charles N. Fisher and Richard J. LeBlanc,
Jr, Crafting A Compiler, The Benjamin Cummings Publishing Company,
1988

\bibitem[Goldberg83]{goldberg83}Adele Goldberg and David Robson,
{\em Smalltalk-80: The language and its Implementation}, Addison-Wesley,
1983

\bibitem[Booch83]{booch83}Grady Booch, {\em Software Engineering with
Ada}, Benjamin Cummings Publishing Co., Menelo Park, 1983

\bibitem[Liskov81]{liskov81}Barbara H. Liskov and Alan Snyder,
``Exception Handling in CLU'', IEEE Trans. on Software Engineering,
vol SE-5, no. 6, pp 546-558

\bibitem[Sakkinen88]{sakkinen88}M. Sakkinen, On the Darker Side of C++'', 
Proceedings of the 1988 European Conference of Object Oriented Programming'',
Springer, 1988

\end{thebibliography}
